PANCHANGE_analysis

### 2020-09-25 PANCHANGE_analysis.Rmd
added regression with baseline only for all measures

@@

@@

@@

>>>>

#GAD baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

# Regression diagnostic statistics
gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_reg_stats)
gad_baseline_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad model0b absolute whole sample}
# Regression coefficients
gad_baseline_model0b_estimates <- model0b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0b_estimates)
gad_baseline_model0b_estimates

# Regression diagnostic statistics
gad_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0b_reg_stats)
gad_baseline_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a absolute whole sample}
# Regression coefficients
gad_baseline_model1a_estimates <- model1a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1a_estimates)
gad_baseline_model1a_estimates

# Regression diagnostic statistics
gad_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1a_reg_stats)
gad_baseline_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

# Regression diagnostic statistics
gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_reg_stats)
gad_baseline_model1b_reg_stats
```

@@

#PHQ baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a absolute whole sample}
# Regression coefficients
phq_baseline_model0a_estimates <- model0a.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model0a_estimates)
phq_baseline_model0a_estimates

# Regression diagnostic statistics
phq_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model0a_reg_stats)
phq_baseline_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b absolute whole sample}
# Regression coefficients
phq_baseline_model0b_estimates <- model0b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model0b_estimates)
phq_baseline_model0b_estimates

# Regression diagnostic statistics
phq_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model0b_reg_stats)
phq_baseline_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a absolute whole sample}
# Regression coefficients
phq_baseline_model1a_estimates <- model1a.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1a_estimates)
phq_baseline_model1a_estimates

# Regression diagnostic statistics
phq_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1a_reg_stats)
phq_baseline_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

# Regression diagnostic statistics
phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_reg_stats)
phq_baseline_model1b_reg_stats
```

@@

# OCI-R baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir model0a absolute whole sample}
# Regression coefficients
ocir_baseline_model0a_estimates <- model0a.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model0a_estimates)
ocir_baseline_model0a_estimates

# Regression diagnostic statistics
ocir_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model0a_reg_stats)
ocir_baseline_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir model0b absolute whole sample}
# Regression coefficients
ocir_baseline_model0b_estimates <- model0b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model0b_estimates)
ocir_baseline_model0b_estimates

# Regression diagnostic statistics
ocir_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model0b_reg_stats)
ocir_baseline_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a absolute whole sample}
# Regression coefficients
ocir_baseline_model1a_estimates <- model1a.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1a_estimates)
ocir_baseline_model1a_estimates

# Regression diagnostic statistics
ocir_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1a_reg_stats)
ocir_baseline_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

# Regression diagnostic statistics
ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_reg_stats)
ocir_baseline_model1b_reg_stats
```

@@

# PCL baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r pcl model0a absolute whole sample}
# Regression coefficients
pcl_baseline_model0a_estimates <- model0a.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model0a_estimates)
pcl_baseline_model0a_estimates

# Regression diagnostic statistics
pcl_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model0a_reg_stats)
pcl_baseline_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r pcl model0b absolute whole sample}
# Regression coefficients
pcl_baseline_model0b_estimates <- model0b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model0b_estimates)
pcl_baseline_model0b_estimates

# Regression diagnostic statistics
pcl_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model0b_reg_stats)
pcl_baseline_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a absolute whole sample}
# Regression coefficients
pcl_baseline_model1a_estimates <- model1a.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1a_estimates)
pcl_baseline_model1a_estimates

# Regression diagnostic statistics
pcl_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1a_reg_stats)
pcl_baseline_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

# Regression diagnostic statistics
pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_reg_stats)
pcl_baseline_model1b_reg_stats
```
